Calendar-based graphics for visualizing people's daily schedules

### 2017-07-26 main.Rmd
embedded rticles in bookdown

keywords:
  # at least one keyword must be supplied
  formatted: [data visualization, statistical graphics, time series, R package, grammar of graphics]
  plain:     [data visualization, statistical graphics, time series, R package, grammar of graphics]
preamble: >
  \usepackage{amsmath}
  \usepackage{tikz}
output: 
  rticles::jss_article:
  citation_package: biblatex
bibliography: ["references.bib", "packages.bib"]
---

@@

```{r ped-map, fig.width = 4, out.width = "0.55\\linewidth", fig.cap = "Map of the Melbourne city with purple dots indicating sensor locations."}
```

```{r time-series-plot, fig.height = 6, fig.cap = "Time series plot about the number of pedestrians in 2016 measured at 3 different sensors in the city of Melbourne. Coloured by the sensors, small multiples of lines show that the foot traffic varies from one sensor to another in terms of both time and number. The weekly patterns look distincitve across these 3 sensors. There is an eye-catching spike which occurred at State Library, caused by the annual event--White Night--on 20th of Feburary."}
```

```{r facet-time, fig.height = 6, fig.cap = "Hourly pedestrian counts facetted by sensors and days of the week using lines. It features at least two types of seasons--time of day and day of week--across all the sensors. The temporal patterns are subject to the sensor locations too."}
```

@@

```{r flinders-2016, fig.height = 6.5, fig.cap = "The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs. The arrangement of the data into a 3 by 4 monthly grid represents all the traffic in 2016. The disparities between weekday and weekend along with public holiday are immediately apparent."}
```

@@

```{r month-diagram, out.width = "360pt", out.height = "250pt", fig.cap = "Illustration of the indexing layout for cells in a month."}
include_graphics("figure/month.pdf")
```

@@

```{r year-diagram, out.width = "360pt", out.height = "250pt", fig.cap = "Illustration of the indexing layout for months of one year."}
include_graphics("figure/year.pdf")
```

@@

Assuming that tidy data [@wickham2014tidy] is the underlying data structure, the parameter \code{x} takes a variable that will be mapped to the x axis and the parameter \code{y} mapped to the y axis for plot construction. In Figure \ref{fig:flinders-2016}, for example, the \code{x} is the variable specifying the time of the day, and the \code{y} is the variable representing the hourly counts. The \code{date} argument is given by the date variable that determines the correct order of the calendar layout.

@@

```{r flinders-polar, fig.height = 6.5, fig.cap = "Star plots of hourly pedestrian counts at Flinders Street Station, which are line charts placed in polar coordinates. The periodic behaviors on workdays are clearly visible."}
```

@@

```{r flinders-free, fig.height = 6.5, fig.cap = "Line glyphs on the calendar format showing hourly foot traffic at Flinders Street Station, scaled over all the days. The individual shape on a single day becomes more distinctive, however it is more difficult to compare the size of peaks between days."}
```

@@

```{r overlay, fig.height = 7, fig.cap = "Overlaying line graphs of the 3 sensors in the monthly calendar. Flagstaff station is not as busy as the other two on non-work days."}
```

@@

```{r facet, fig.height = 11, fig.cap = "Line charts, embedded in the 6 by 2 monthly calendar, coloured and faceted by the 3 sensors. The variations of an individual sensor are emphasised, and the shapes can be compared across the cells and sensors."}
```

@@

```{r scatterplot, fig.height = 5, fig.cap = "Lag scatterplot in the daily calendar layout. Previous hour's count is plotted against each hour's count at Flinders Street Station to demonstrate the autocorrelation at lag 1. The correlation between them is more consistent on non-work days than work days."}
```

The newly computed coordinates can work with more complicated plots, such as the boxplot. Figure \ref{fig:boxplot} uses the loess smooth line superimposed on side-by-side boxplots. It shows the distribution of hourly counts across all 43 sensors during December. In general, bimodality features on work days whereas unimodality features on the rest of the days. The last week of December is the holiday season: people are off work on the day before Christmas, go shopping on the Boxing day, and stay out for the fireworks on New Year's Eve.

```{r boxplot, fig.height = 6.5, fig.cap = "Side-by-side boxplot of hourly counts across all the 43 sensors in December of 2016, with the superimposing loess smooth line for each day. It shows the hourly distribution in the city as a whole. Christmas stands out as the quietest day in December."}
```

```{r chn, dev.args = list(family = "GB1"), fig.height = 6.5, fig.cap = "Figure 12 with Chinese text labels."}
```

>>>>

keywords:
  # at least one keyword must be supplied
  formatted: [data visualization, statistical graphics, time series, R package, grammar of graphics]
  plain:     [data visualization, statistical graphics, time series, R package, grammar of graphics]
preamble: >
  \usepackage{amsmath}
  \usepackage{tikz}
output: 
  bookdown::pdf_book:
    base_format: rticles::jss_article
  citation_package: biblatex
bibliography: ["references.bib", "packages.bib"]
---

@@

```{r ped-map, fig.width = 4, out.width = "0.55\\linewidth", fig.cap = "(ref:ped-map-cap)"}
```

(ref:ped-map-cap) Map of the Melbourne city with purple dots indicating sensor locations.

```{r time-series-plot, fig.height = 6, fig.cap = "(ref:time-series-plot-cap)"}
```

(ref:time-series-plot-cap) Time series plot about the number of pedestrians in 2016 measured at 3 different sensors in the city of Melbourne. Coloured by the sensors, small multiples of lines show that the foot traffic varies from one sensor to another in terms of both time and number. The weekly patterns look distinctive across these 3 sensors. There is an eye-catching spike which occurred at State Library, caused by the annual event--White Night--on 20th of February.

```{r facet-time, fig.height = 6, fig.cap = "(ref:facet-time-cap)"}
```

(ref:facet-time-cap) Hourly pedestrian counts faceted by sensors and days of the week using lines. It features at least two types of seasons--time of day and day of week--across all the sensors. The temporal patterns are subject to the sensor locations too.

@@

```{r flinders-2016, fig.height = 6.5, fig.cap = "(ref:flinders-2016-cap)"}
```

(ref:flinders-2016-cap) The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs. The arrangement of the data into a 3 by 4 monthly grid represents all the traffic in 2016. The disparities between weekday and weekend along with public holiday are immediately apparent.

@@

```{r month-diagram, out.width = "360pt", out.height = "250pt", fig.cap = "(ref:month-diagram-cap)"}
include_graphics("figure/month.pdf")
```

(ref:month-diagram-cap) Illustration of the indexing layout for cells in a month.

@@

```{r year-diagram, out.width = "360pt", out.height = "250pt", fig.cap = "(ref:year-diagram-cap)"}
include_graphics("figure/year.pdf")
```

(ref:year-diagram-cap) Illustration of the indexing layout for months of one year.

@@

Assuming that tidy data [@wickham2014tidy] is the underlying data structure, the parameter \code{x} takes a variable that will be mapped to the horizontal axis and the parameter \code{y} mapped to the vertical axis for plot construction. In Figure \ref{fig:flinders-2016}, for example, the \code{x} is the variable specifying the time of the day, and the \code{y} is the variable representing the hourly counts. The \code{date} argument is given by the date variable that determines the correct order of the calendar layout.

@@

```{r flinders-polar, fig.height = 6.5, fig.cap = "(ref:flinders-polar-cap)"}
```

(ref:flinders-polar-cap) Star plots of hourly pedestrian counts at Flinders Street Station, which are line charts placed in polar coordinates. The periodic behaviors on workdays are clearly visible.

@@

```{r flinders-free, fig.height = 6.5, fig.cap = "(ref:flinders-free-cap)"}
```

(ref:flinders-free-cap) Line glyphs on the calendar format showing hourly foot traffic at Flinders Street Station, scaled over all the days. The individual shape on a single day becomes more distinctive, however it is more difficult to compare the size of peaks between days.

@@

```{r overlay, fig.height = 7, fig.cap = "(ref:overlay-cap)"}
```

(ref:overlay-cap) Overlaying line graphs of the 3 sensors in the monthly calendar. Flagstaff station is not as busy as the other two on non-work days.

@@

```{r facet, fig.height = 11, fig.cap = "(ref:facet-cap)"}
```

(ref:facet-cap) Line charts, embedded in the 6 by 2 monthly calendar, coloured and faceted by the 3 sensors. The variations of an individual sensor are emphasised, and the shapes can be compared across the cells and sensors.

@@

```{r scatterplot, fig.height = 5, fig.cap = "(ref:scatterplot-cap)"}
```

(ref:scatterplot-cap) Lag scatterplot in the daily calendar layout. Previous hour's count is plotted against each hour's count at Flinders Street Station to demonstrate the autocorrelation at lag 1. The correlation between them is more consistent on non-work days than work days.

The newly computed coordinates can work with more complicated plots, such as the boxplot. Figure \ref{fig:boxplot} uses the loess smooth line superimposed on side-by-side boxplots. It shows the distribution of hourly counts across all 43 sensors at a given time point during December. In general, bimodality features on work days whereas unimodality features on the rest of the days. The last week of December is the holiday season: people are off work on the day before Christmas, go shopping on the Boxing day, and stay out for the fireworks on New Year's Eve.

```{r boxplot, fig.height = 6.5, fig.cap = "(ref:boxplot-cap)"}
```

(ref:boxplot-cap) Side-by-side boxplot of hourly counts across all the 43 sensors in December of 2016, with the superimposing loess smooth line for each day. It shows the hourly distribution in the city as a whole. Christmas stands out as the quietest day in December.

```{r chn, dev.args = list(family = "GB1"), fig.height = 6.5, fig.cap = "(ref:chn-cap)"}
```

(ref:chn-cap) Figure \ref{fig:boxplot} with Chinese text labels.

### 2017-07-26 main.tex
embedded rticles in bookdown

\begin{document}

@@

\caption[Map of the Melbourne city with purple dots indicating sensor locations]{Map of the Melbourne city with purple dots indicating sensor locations.}\label{fig:ped-map}
\end{figure}
\end{CodeChunk}

@@

\caption[Time series plot about the number of pedestrians in 2016 measured at 3 different sensors in the city of Melbourne]{Time series plot about the number of pedestrians in 2016 measured at 3 different sensors in the city of Melbourne. Coloured by the sensors, small multiples of lines show that the foot traffic varies from one sensor to another in terms of both time and number. The weekly patterns look distincitve across these 3 sensors. There is an eye-catching spike which occurred at State Library, caused by the annual event--White Night--on 20th of Feburary.}\label{fig:time-series-plot}
\end{figure}
\end{CodeChunk}

@@

\caption[Hourly pedestrian counts facetted by sensors and days of the week using lines]{Hourly pedestrian counts facetted by sensors and days of the week using lines. It features at least two types of seasons--time of day and day of week--across all the sensors. The temporal patterns are subject to the sensor locations too.}\label{fig:facet-time}
\end{figure}
\end{CodeChunk}

@@

\caption[The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs]{The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs. The arrangement of the data into a 3 by 4 monthly grid represents all the traffic in 2016. The disparities between weekday and weekend along with public holiday are immediately apparent.}\label{fig:flinders-2016}
\end{figure}
\end{CodeChunk}

@@

\caption[Illustration of the indexing layout for cells in a month]{Illustration of the indexing layout for cells in a month.}\label{fig:month-diagram}
\end{figure}
\end{CodeChunk}

@@

\caption[Illustration of the indexing layout for months of one year]{Illustration of the indexing layout for months of one year.}\label{fig:year-diagram}
\end{figure}
\end{CodeChunk}

@@

Assuming that tidy data \citep{wickham2014tidy} is the underlying data
structure, the parameter \code{x} takes a variable that will be mapped
to the x axis and the parameter \code{y} mapped to the y axis for plot
construction. In Figure \ref{fig:flinders-2016}, for example, the
\code{x} is the variable specifying the time of the day, and the
\code{y} is the variable representing the hourly counts. The \code{date}
argument is given by the date variable that determines the correct order
of the calendar layout.

@@

\caption[Star plots of hourly pedestrian counts at Flinders Street Station, which are line charts placed in polar coordinates]{Star plots of hourly pedestrian counts at Flinders Street Station, which are line charts placed in polar coordinates. The periodic behaviors on workdays are clearly visible.}\label{fig:flinders-polar}
\end{figure}
\end{CodeChunk}

@@

\caption[Line glyphs on the calendar format showing hourly foot traffic at Flinders Street Station, scaled over all the days]{Line glyphs on the calendar format showing hourly foot traffic at Flinders Street Station, scaled over all the days. The individual shape on a single day becomes more distinctive, however it is more difficult to compare the size of peaks between days.}\label{fig:flinders-free}
\end{figure}
\end{CodeChunk}

@@

\caption[Overlaying line graphs of the 3 sensors in the monthly calendar]{Overlaying line graphs of the 3 sensors in the monthly calendar. Flagstaff station is not as busy as the other two on non-work days.}\label{fig:overlay}
\end{figure}
\end{CodeChunk}

@@

\caption[Line charts, embedded in the 6 by 2 monthly calendar, coloured and faceted by the 3 sensors]{Line charts, embedded in the 6 by 2 monthly calendar, coloured and faceted by the 3 sensors. The variations of an individual sensor are emphasised, and the shapes can be compared across the cells and sensors.}\label{fig:facet}
\end{figure}
\end{CodeChunk}

@@

\caption[Lag scatterplot in the daily calendar layout]{Lag scatterplot in the daily calendar layout. Previous hour's count is plotted against each hour's count at Flinders Street Station to demonstrate the autocorrelation at lag 1. The correlation between them is more consistent on non-work days than work days.}\label{fig:scatterplot}
\end{figure}
\end{CodeChunk}

The newly computed coordinates can work with more complicated plots,
such as the boxplot. Figure \ref{fig:boxplot} uses the loess smooth line
superimposed on side-by-side boxplots. It shows the distribution of
hourly counts across all 43 sensors during December. In general,
bimodality features on work days whereas unimodality features on the
rest of the days. The last week of December is the holiday season:
people are off work on the day before Christmas, go shopping on the
Boxing day, and stay out for the fireworks on New Year's Eve.

@@

\caption[Side-by-side boxplot of hourly counts across all the 43 sensors in December of 2016, with the superimposing loess smooth line for each day]{Side-by-side boxplot of hourly counts across all the 43 sensors in December of 2016, with the superimposing loess smooth line for each day. It shows the hourly distribution in the city as a whole. Christmas stands out as the quietest day in December.}\label{fig:boxplot}
\end{figure}
\end{CodeChunk}

@@

\caption[Figure 12 with Chinese text labels]{Figure 12 with Chinese text labels.}\label{fig:chn}
\end{figure}
\end{CodeChunk}

>>>>

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\begin{document}

@@

\caption[Map of the Melbourne city with purple dots indicating
sensor locations.]{Map of the Melbourne city with purple dots indicating
sensor locations.}\label{fig:ped-map}
\end{figure}
\end{CodeChunk}

@@

\caption[Time series plot about the number of
pedestrians in 2016 measured at 3 different sensors in the city of
Melbourne. Coloured by the sensors, small multiples of lines show that
the foot traffic varies from one sensor to another in terms of both time
and number. The weekly patterns look distinctive across these 3 sensors.
There is an eye-catching spike which occurred at State Library, caused
by the annual event--White Night--on 20th of February.]{Time series plot about the number of
pedestrians in 2016 measured at 3 different sensors in the city of
Melbourne. Coloured by the sensors, small multiples of lines show that
the foot traffic varies from one sensor to another in terms of both time
and number. The weekly patterns look distinctive across these 3 sensors.
There is an eye-catching spike which occurred at State Library, caused
by the annual event--White Night--on 20th of February.}\label{fig:time-series-plot}
\end{figure}
\end{CodeChunk}

@@

\caption[Hourly pedestrian counts faceted by sensors and
days of the week using lines. It features at least two types of
seasons--time of day and day of week--across all the sensors. The
temporal patterns are subject to the sensor locations too.]{Hourly pedestrian counts faceted by sensors and
days of the week using lines. It features at least two types of
seasons--time of day and day of week--across all the sensors. The
temporal patterns are subject to the sensor locations too.}\label{fig:facet-time}
\end{figure}
\end{CodeChunk}

@@

\caption[The calendar-based display of hourly foot
traffic at Flinders Street Station using line glyphs. The arrangement of
the data into a 3 by 4 monthly grid represents all the traffic in 2016.
The disparities between weekday and weekend along with public holiday
are immediately apparent.]{The calendar-based display of hourly foot
traffic at Flinders Street Station using line glyphs. The arrangement of
the data into a 3 by 4 monthly grid represents all the traffic in 2016.
The disparities between weekday and weekend along with public holiday
are immediately apparent.}\label{fig:flinders-2016}
\end{figure}
\end{CodeChunk}

@@

\caption[Illustration of the indexing layout for cells in
a month.]{Illustration of the indexing layout for cells in
a month.}\label{fig:month-diagram}
\end{figure}
\end{CodeChunk}

@@

\caption[Illustration of the indexing layout for months of
one year.]{Illustration of the indexing layout for months of
one year.}\label{fig:year-diagram}
\end{figure}
\end{CodeChunk}

@@

Assuming that tidy data \citep{wickham2014tidy} is the underlying data
structure, the parameter \code{x} takes a variable that will be mapped
to the horizontal axis and the parameter \code{y} mapped to the vertical
axis for plot construction. In Figure \ref{fig:flinders-2016}, for
example, the \code{x} is the variable specifying the time of the day,
and the \code{y} is the variable representing the hourly counts. The
\code{date} argument is given by the date variable that determines the
correct order of the calendar layout.

@@

\caption[Star plots of hourly pedestrian counts at
Flinders Street Station, which are line charts placed in polar
coordinates. The periodic behaviors on workdays are clearly visible.]{Star plots of hourly pedestrian counts at
Flinders Street Station, which are line charts placed in polar
coordinates. The periodic behaviors on workdays are clearly visible.}\label{fig:flinders-polar}
\end{figure}
\end{CodeChunk}

@@

\caption[Line glyphs on the calendar format showing
hourly foot traffic at Flinders Street Station, scaled over all the
days. The individual shape on a single day becomes more distinctive,
however it is more difficult to compare the size of peaks between days.]{Line glyphs on the calendar format showing
hourly foot traffic at Flinders Street Station, scaled over all the
days. The individual shape on a single day becomes more distinctive,
however it is more difficult to compare the size of peaks between days.}\label{fig:flinders-free}
\end{figure}
\end{CodeChunk}

@@

\caption[Overlaying line graphs of the 3 sensors in the monthly
calendar. Flagstaff station is not as busy as the other two on non-work
days.]{Overlaying line graphs of the 3 sensors in the monthly
calendar. Flagstaff station is not as busy as the other two on non-work
days.}\label{fig:overlay}
\end{figure}
\end{CodeChunk}

@@

\caption[Line charts, embedded in the 6 by 2 monthly calendar,
coloured and faceted by the 3 sensors. The variations of an individual
sensor are emphasised, and the shapes can be compared across the cells
and sensors.]{Line charts, embedded in the 6 by 2 monthly calendar,
coloured and faceted by the 3 sensors. The variations of an individual
sensor are emphasised, and the shapes can be compared across the cells
and sensors.}\label{fig:facet}
\end{figure}
\end{CodeChunk}

@@

\caption[Lag scatterplot in the daily calendar layout.
Previous hour's count is plotted against each hour's count at Flinders
Street Station to demonstrate the autocorrelation at lag 1. The
correlation between them is more consistent on non-work days than work
days.]{Lag scatterplot in the daily calendar layout.
Previous hour's count is plotted against each hour's count at Flinders
Street Station to demonstrate the autocorrelation at lag 1. The
correlation between them is more consistent on non-work days than work
days.}\label{fig:scatterplot}
\end{figure}
\end{CodeChunk}

The newly computed coordinates can work with more complicated plots,
such as the boxplot. Figure \ref{fig:boxplot} uses the loess smooth line
superimposed on side-by-side boxplots. It shows the distribution of
hourly counts across all 43 sensors at a given time point during
December. In general, bimodality features on work days whereas
unimodality features on the rest of the days. The last week of December
is the holiday season: people are off work on the day before Christmas,
go shopping on the Boxing day, and stay out for the fireworks on New
Year's Eve.

@@

\caption[Side-by-side boxplot of hourly counts across all the
43 sensors in December of 2016, with the superimposing loess smooth line
for each day. It shows the hourly distribution in the city as a whole.
Christmas stands out as the quietest day in December.]{Side-by-side boxplot of hourly counts across all the
43 sensors in December of 2016, with the superimposing loess smooth line
for each day. It shows the hourly distribution in the city as a whole.
Christmas stands out as the quietest day in December.}\label{fig:boxplot}
\end{figure}
\end{CodeChunk}

@@

\caption[Figure \ref{fig:boxplot} with Chinese text labels.]{Figure \ref{fig:boxplot} with Chinese text labels.}\label{fig:chn}
\end{figure}
\end{CodeChunk}
